Video Understanding : A review of action detection-recognition dataset

### 2024-02-16 paper.tex
updated

It includes 6,766 video clips covering 51 different action categories sourced from movies and Internet, with each category having at least 101 clips. Each video contains a single action described in its name, with a quality of 240px and length of more than 1 second.
\subsection{UCF101}
Introduced in 2012 as an expansion of UCF50 by adding 51 classes, UCF101 aimed to refine and expand the range of actions captured in the previous datasets, contributing to a more comprehensive understanding of human activities. Additionally, the dataset also blurs the difference between artificial and real-life videos, therefore accurately reflects the diversity of human actions represented in real-world scenarios. Among the four versions of the UCF family: "UCF Sports, UCF11, UCF50, and UCF101", the dataset being referred to is the largest and most widely used.

The dataset contains 13,320 videos demonstrating 101 actions. Each clip has a resolution of 320x240 pixels at 25 FPS. Additionally, this dataset also includes audio data for 50 action classes. Each clip has its augmented version, which expands into various variants of itself, such as increasing or reducing the length, changing the segment, or adding audio.
\subsection{Sport-1M}
In 2014, Sport-1M was developed to apply CNN methods to action recognition categories, marking a departure from datasets such as HMDB51 and UCF101, which were designed to accommodate traditional machine learning methods, especially SVM, thus became non-equivalent. Therefore, with the rise of CNNs, there has been encouragement to develop equivalent resources that can enhance their capabilities.

The dataset contains 1,133,158 YouTube videos, covering a diverse range of content. There are 487 unique classes in the dataset, with each class ranging from 1000 to 3000 videos. Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5\% of the dataset.
\subsection{ActivityNet}
First introduced in 2015, ActivityNet offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure. At that time, UCF101 and THUMOS-14 already have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide. This hierarchical organization allows for a detailed understanding of the diverse range of behaviors captured in this dataset, especially in every day activities.

In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities. Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720). 
\subsection{Something Something}
Introduced its first version in 2017, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M or YouTube-8M, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects. 
\subsection{Charades}
Introduced in 2016, Charades is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 and UCF101, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
\subsection{Youtube-8M}
In 2016, YouTube-8M was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method. Unlike previous datasets such as Sports-1M and ActivityNet, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities. The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.

In the newest update in May 2018, YouTube-8M underwent a cleanup process to ensure quality for both video resolution and annotation vocabulary. It removed the private, unfamous and sensitive contents for safety purpose. Currently, the dataset comprises over 6.1 million video IDs from 3,862 entities, grouped into 24 high-level topics. Each video is required to be between 120 and 500 seconds long and must contain at least one target vocabulary. The dataset allows for multi-label assignments, with each video typically having an average of 3.0 assigned classes. 
\subsection{AVA}
Introduced in 2018, AVA's main goal is to overcome weaknesses of previous datasets like Sports-1M, YouTube-8M, Something Something, and Moments in Time, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet, THUMOS, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

Currently, there are four different versions of AVA. The newest version, v2.2, consists of a total of 430 videos covering 80 classes extracted from movies. Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.
\subsection{Moments in Time}
In 2019, Moments in Time was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds. Over the years, the rapid growth of datasets has expanded the usability of human action understanding. Large-scale video datasets such as Kinetics and YouTube-8M play significant roles in studying open-world vocabulary from the internet. Other datasets, such as ActivityNet and AVA, explore recognizing and localizing fine-grained actions by linking correlations. To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.

The dataset contains more than 1,000,000 labeled 3-second videos, which include 339 action classes. The actors performing actions are not just limited to humans but also include animals or cartoon characters. Therefore, this dataset proposes a new challenge in recognizing events across various actors. Moreover, sound-dependent classes are added to expand the capability of understanding auditory cues.
\subsection{HACS}
HACS emerged in response to the increasing need for extensive datasets, facilitating the development of more sophisticated models in the realm of action recognition. Inspired by the notable expansions witnessed in large-scale action recognition datasets like Sport-1M, Kinetics, and Moments in Time, HACS enhances both its scale and quality to offer a more encompassing resource. Moreover, it builds upon the strengths of past action localization datasets such as THUMOS, AVA, Charades, and especially ActivityNet.

The dataset provides 504K videos sourced from YouTube, categorized into 200 action classes. These videos are trimmed into shorter segments, resulting in a total of 1.5M clips, each lasting 2 seconds, for more accurate labeling which is called HACS Segments. Then, it is annotated into positive (has action) and negative (doesn't has action) samples.
\subsection{HVU}
Introduced in 2020 as a multi-label and multi-task fully annotated dataset, HVU provides a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding. CNNs model has envolved to be stronger and faster in recent years, but the datasets just allow them to recognize single label per task, which hinders the learning of ConvNets.

HVU comprises a total of 572,000 videos and 3,143 labels. It consists of trimmed video clips with varying durations, capped at a maximum length of 10 seconds. Additionally, HVU does not solely rely on a single action class but instead includes multiple tags which is organized into six main categories: scene, object, action, event, attribute, and concept.
\subsection{AViD}
Introduced in 2020, AViD aims to provide an Anonymized Videos from Diverse Countries dataset. In the past, datasets such as Kinetics, HACS, and HVU, although containing numerous labeled video clips, were predominantly limited to the USA and other English-speaking countries. Moreover, those datasets were mainly sourced from YouTube links, which may not be available in some countries. AViD solves that problem by saving it as a static dataset, which can be found at the relevant link provided by the authors. When collecting videos, the authors blurred all the actors' faces to prevent machines from recognizing people in the videos but still reliably recognized actions, which is also a unique characteristic of this dataset.

>>>>

It includes 6,766 video clips covering 51 different action categories sourced from movies and Internet, with each category having at least 101 clips. Each video contains a single action described in its name, with a quality of 240px and length of more than 1 second.
\subsection{UCF101}
Introduced in 2012 as an expansion of UCF50 by adding 51 classes, UCF101 \cite{UCF101} aimed to refine and expand the range of actions captured in the previous datasets, contributing to a more comprehensive understanding of human activities. Additionally, the dataset also blurs the difference between artificial and real-life videos, therefore accurately reflects the diversity of human actions represented in real-world scenarios. Among the four versions of the UCF family: "UCF Sports \cite{UCFSports}, UCF11 \cite{UCFYouTube}, UCF50, and UCF101", the dataset being referred to is the largest and most widely used.

The dataset contains 13,320 videos demonstrating 101 actions. Each clip has a resolution of 320x240 pixels at 25 FPS. Additionally, this dataset also includes audio data for 50 action classes. Each clip has its augmented version, which expands into various variants of itself, such as increasing or reducing the length, changing the segment, or adding audio.
\subsection{Sport-1M}
In 2014, Sport-1M \cite{Sports1M} was developed to apply CNN methods to action recognition categories, marking a departure from datasets such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, which were designed to accommodate traditional machine learning methods, especially SVM, thus became non-equivalent. Therefore, with the rise of CNNs, there has been encouragement to develop equivalent resources that can enhance their capabilities.

The dataset contains 1,133,158 YouTube videos, covering a diverse range of content. There are 487 unique classes in the dataset, with each class ranging from 1000 to 3000 videos. Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5\% of the dataset.
\subsection{ActivityNet}
First introduced in 2015, ActivityNet \cite{ActivityNet} offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure. At that time, UCF101 \cite{UCF101} and THUMOS-14 \cite{THUMOS} already have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide. This hierarchical organization allows for a detailed understanding of the diverse range of behaviors captured in this dataset, especially in every day activities.

In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities. Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720). 
\subsection{Youtube-8M}
In 2016, YouTube-8M \cite{YouTube8M} was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method. Unlike previous datasets such as Sports-1M \cite{Sports1M} and ActivityNet \cite{ActivityNet}, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities. The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.

In the newest update in May 2018, YouTube-8M underwent a cleanup process to ensure quality for both video resolution and annotation vocabulary. It removed the private, unfamous and sensitive contents for safety purpose. Currently, the dataset comprises over 6.1 million video IDs from 3,862 entities, grouped into 24 high-level topics. Each video is required to be between 120 and 500 seconds long and must contain at least one target vocabulary. The dataset allows for multi-label assignments, with each video typically having an average of 3.0 assigned classes.

\subsection{Something Something}
Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects. 
\subsection{Charades}
Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.

\subsection{AVA}
Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

Currently, there are four different versions of AVA. The newest version, v2.2, consists of a total of 430 videos covering 80 classes extracted from movies. Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.
\subsection{Moments in Time}
In 2019, Moments in Time \cite{momentsintime} was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds. Over the years, the rapid growth of datasets has expanded the usability of human action understanding. Large-scale video datasets such as Kinetics and YouTube-8M \cite{YouTube8M} play significant roles in studying open-world vocabulary from the internet. Other datasets, such as ActivityNet \cite{ActivityNet} and AVA \cite{AVA}, explore recognizing and localizing fine-grained actions by linking correlations. To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.

The dataset contains more than 1,000,000 labeled 3-second videos, which include 339 action classes. The actors performing actions are not just limited to humans but also include animals or cartoon characters. Therefore, this dataset proposes a new challenge in recognizing events across various actors. Moreover, sound-dependent classes are added to expand the capability of understanding auditory cues.
\subsection{HACS}
HACS \cite{HACS} emerged in response to the increasing need for extensive datasets, facilitating the development of more sophisticated models in the realm of action recognition. Inspired by the notable expansions witnessed in large-scale action recognition datasets like Sport-1M, Kinetics, and Moments in Time, HACS enhances both its scale and quality to offer a more encompassing resource. Moreover, it builds upon the strengths of past action localization datasets such as THUMOS \cite{THUMOS}, AVA \cite{AVA}, Charades \cite{Charades}, and especially ActivityNet \cite{ActivityNet}.

The dataset provides 504K videos sourced from YouTube, categorized into 200 action classes. These videos are trimmed into shorter segments, resulting in a total of 1.5M clips, each lasting 2 seconds, for more accurate labeling which is called HACS Segments. Then, it is annotated into positive (has action) and negative (doesn't has action) samples.
\subsection{HVU}
Introduced in 2020 as a multi-label and multi-task fully annotated dataset, HVU \cite{HVU} provides a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding. CNNs model has envolved to be stronger and faster in recent years, but the datasets just allow them to recognize single label per task, which hinders the learning of ConvNets.

HVU comprises a total of 572,000 videos and 3,143 labels. It consists of trimmed video clips with varying durations, capped at a maximum length of 10 seconds. Additionally, HVU does not solely rely on a single action class but instead includes multiple tags which is organized into six main categories: scene, object, action, event, attribute, and concept.
\subsection{AViD}
Introduced in 2020, AViD \cite{AViD} aims to provide an Anonymized Videos from Diverse Countries dataset. In the past, datasets such as Kinetics, HACS \cite{HACS}, and HVU \cite{HVU}, although containing numerous labeled video clips, were predominantly limited to the USA and other English-speaking countries. Moreover, those datasets were mainly sourced from YouTube links, which may not be available in some countries. AViD solves that problem by saving it as a static dataset, which can be found at the relevant link provided by the authors. When collecting videos, the authors blurred all the actors' faces to prevent machines from recognizing people in the videos but still reliably recognized actions, which is also a unique characteristic of this dataset.
